---
title: "The Consumer Credit Sourcebook – Chapter Summaries"
author: "Martien Lubberink"
date: today
freeze: false
format:
  html:
    theme: cosmo
    toc: true
    toc-depth: 2
    anchor-sections: true
    df-print: paged
    css: |
      <style>
      .priority-essential { background:#d4edda; color:#155724; padding:3px 10px; border-radius:4px; font-weight:bold; }
      .priority-important { background:#fff3cd; color:#856404; padding:3px 10px; border-radius:4px; font-weight:bold; }
      .priority-optional { background:#f8d7da; color:#721c24; padding:3px 10px; border-radius:4px; }
      .score-bar { background: linear-gradient(90deg, #28a745 0%, #ffc107 50%, #dc3545 100%); height: 8px; border-radius: 4px; margin-top: 2px; }
      </style>
page-layout: article
---

## Overview

This page provides downloadable summaries of chapters from the [Consumer Credit Sourcebook](https://www.handbook.fca.org.uk/handbook/CONC.pdf) ([CONC](https://www.handbook.fca.org.uk/handbook/CONC/1/1.html)), analyzed for relevance to the Central Bank of Nigeria (CBN) regulatory framework.

The entire CONC is over 400 pages, making it tricky to convert into a single CBN chapter. By breaking it into chapters and assessing relevance, the work can be prioritized effectively. Chapter 7 was split into two parts due to its size.

```{r}
#| label: setup
#| include: false

library(jsonlite)
library(knitr)

# Helper: human-readable file sizes
fmt_size <- function(bytes) {
  units <- c("B","KB","MB","GB","TB")
  if (is.na(bytes) || is.null(bytes)) return(NA_character_)
  pow <- ifelse(bytes > 0, floor(log(bytes, 1024)), 0)
  pow <- pmin(pow, length(units) - 1)
  sprintf("%.1f %s", bytes/(1024^pow), units[pow+1])
}

# Load relevance data if available
relevance_data <- NULL
if (file.exists("cbn_relevance_assessment.json")) {
  relevance_data <- fromJSON("cbn_relevance_assessment.json")
}
```

## Quick Downloads

:::: {.callout-tip}
## Complete Collections
For convenience, download all summaries and assessments in single files:

```{r}
#| label: quick-downloads
#| echo: false
#| warning: false
#| message: false
#| results: asis

collections <- list(
  list(file = "CBN_All_Summaries.docx", icon = "📄", desc = "Complete summary collection"),
  list(file = "CBN_relevance_report.docx", icon = "📋", desc = "Detailed relevance report"),
  list(file = "CBN_relevance_assessment.xlsx", icon = "📊", desc = "Relevance assessment spreadsheet")
)

for (item in collections) {
  if (file.exists(item$file)) {
    info <- file.info(item$file)
    cat(sprintf(
      "- %s [**%s**](%s) <span style='color:#666;font-size:0.9em'>(%s)</span>\n",
      item$icon, item$desc, item$file, fmt_size(info$size)
    ))
  }
}
```
::::

## Original pdfs and Chapter Summaries

```{r}
#| label: build-table
#| echo: false
#| warning: false
#| message: false

# List files
md_files   <- list.files(pattern = "^ch_.*_summary\\.md$", ignore.case = TRUE)
docx_files <- list.files(pattern = "^ch_.*_summary\\.docx$", ignore.case = TRUE)

# Get base names
base_md   <- sub("\\.md$", "", md_files, ignore.case = TRUE)
base_docx <- sub("\\.docx$", "", docx_files, ignore.case = TRUE)
bases <- sort(unique(c(base_md, base_docx)))

# Build data frame
rows <- lapply(bases, function(b) {
  md   <- paste0(b, ".md")
  docx <- paste0(b, ".docx")
  
  md_exists   <- file.exists(md)
  docx_exists <- file.exists(docx)
  
  # Extract chapter name
  chapter_raw <- gsub("^ch_([^_]+).*", "\\1", b)
  chapter <- toupper(chapter_raw)
  
  # Get relevance info if available
  priority <- "—"
  score <- "—"
  score_num <- 0
  key_topic <- ""
  
  if (!is.null(relevance_data)) {
    # Try to match with different formats
    matching <- relevance_data[relevance_data$chapter == paste0("ch_", chapter_raw), ]
    if (nrow(matching) == 0) {
      matching <- relevance_data[relevance_data$chapter == chapter_raw, ]
    }
    
    if (nrow(matching) > 0) {
      priority <- matching$priority_level[1]
      score_num <- matching$relevance_score[1]
      score <- paste0(score_num, "/10")
      if (!is.null(matching$key_topics) && length(matching$key_topics[[1]]) > 0) {
        key_topic <- matching$key_topics[[1]][1]
      }
    }
  }
  
  # Style priority badge
  priority_badge <- switch(priority,
    "Essential" = sprintf('<span class="priority-essential">%s</span>', priority),
    "Important" = sprintf('<span class="priority-important">%s</span>', priority),
    "Optional" = sprintf('<span class="priority-optional">%s</span>', priority),
    priority
  )
  
  # Format chapter display
  chapter_display <- switch(chapter,
    "AX01PDF" = "Annex 1",
    "AXTRPDF" = "Annex TR",
    sprintf("Ch %s", chapter)
  )
  
  # Check for PDF file
  pdf_base <- gsub("_summary$", "", b)
  pdf <- paste0(pdf_base, ".pdf")
  pdf_exists <- file.exists(pdf)
  
  # Build download links with better formatting
  download_links <- c()
  if (pdf_exists) download_links <- c(download_links, sprintf('[📕 PDF](%s)', pdf))
  if (md_exists) download_links <- c(download_links, sprintf('[📝 MD](%s)', md))
  if (docx_exists) download_links <- c(download_links, sprintf('[📄 Word](%s)', docx))
  downloads <- paste(download_links, collapse = " ")
  
  # Get file info for update time
  updated <- as.POSIXct(NA)
  if (md_exists) {
    info <- file.info(md)
    updated <- info$mtime
  }
  if (docx_exists) {
    info <- file.info(docx) 
    updated <- max(updated, info$mtime, na.rm = TRUE)
  }
  
  # Truncate long key topics
  if (nchar(key_topic) > 45) {
    key_topic <- paste0(substr(key_topic, 1, 42), "...")
  }
  
  data.frame(
    Chapter = sprintf("**%s**", chapter_display),
    Priority = priority_badge,
    Score = score,
    score_num = score_num,
    `Key Focus` = key_topic,
    Downloads = downloads,
    Updated = if(is.na(updated)) "" else format(updated, "%b %d"),
    stringsAsFactors = FALSE,
    check.names = FALSE
  )
})

df <- do.call(rbind, rows)

# Sort by score (descending), then by chapter
#if (!is.null(relevance_data)) {
#  df <- df[order(-df$score_num, df$Chapter), ]
  #df <- df[order(df$Chapter), ]
#}

# Remove the score_num column before display
df$score_num <- NULL

# Render table
kable(
  df,
  align = c("l", "c", "c", "l", "c", "r"),
  escape = FALSE
)
```

## Priority Guide

:::: {.panel-tabset}

### 🟢 Essential Chapters
**Direct application to CBN's core mandate** (Score: 8/10)

These chapters contain critical regulatory frameworks:
- Banking supervision and prudential guidelines
- Capital requirements and solvency standards
- Core compliance procedures and reporting
- Consumer protection and fair lending practices

*Recommended: Implement these chapters first with minimal adaptation*

### 🟡 Important Chapters  
**Valuable frameworks requiring adaptation** (Score: 6-7/10)

These chapters provide supporting regulatory concepts:
- Specific banking area regulations (overdrafts, credit cards)
- Risk management and monitoring frameworks
- Agent banking and third-party oversight
- Fee transparency and disclosure requirements

*Recommended: Adapt these to Nigerian banking context*

### 🔴 Optional Chapters
**Reference material for specific cases** (Score: <6/10)

These chapters have limited direct application:
- UK-specific transitional provisions
- Specialized products (rent-to-own)
- Narrow regulatory exemptions
- Historical implementation guidance

*Recommended: Reference only when needed for specific issues*
::::

## Statistics Summary

```{r}
#| label: statistics
#| echo: false
#| warning: false
#| message: false
#| results: asis

if (!is.null(relevance_data)) {
  essential_count <- sum(relevance_data$priority_level == "Essential")
  important_count <- sum(relevance_data$priority_level == "Important")
  optional_count <- sum(relevance_data$priority_level == "Optional")
  avg_score <- mean(relevance_data$relevance_score)
  
  cat(":::: {.callout-note}\n")
  cat("## Assessment Summary\n\n")
  cat(sprintf("- **Total Chapters Analyzed:** %d\n", nrow(relevance_data)))
  cat(sprintf("- **Average Relevance Score:** %.1f/10\n", avg_score))
  cat(sprintf("- **Distribution:** %d Essential, %d Important, %d Optional\n", 
              essential_count, important_count, optional_count))
  cat(sprintf("- **High Priority Chapters (Score ≥8):** %d\n", 
              sum(relevance_data$relevance_score >= 8)))
  cat("::::\n")
}
```

## Usage Notes

:::: {.columns}
::: {.column width="33%"}
### 📕 PDF Files (.pdf)
Original source chapters:
- Complete regulatory text
- Official formatting preserved
- Full detail and footnotes
- Legal reference (~150-230 KB)
- Authoritative source
:::

::: {.column width="33%"}
### 📝 Markdown Files (.md)
AI-generated summaries:
- Version control friendly
- Easy editing and conversion
- Key points extracted
- Lightweight (~3-5 KB)
- GitHub integration
:::

::: {.column width="34%"}
### 📄 Word Documents (.docx)
Formatted summaries:
- Professional presentation
- Track changes support
- Print-ready summaries
- Stakeholder sharing (~38 KB)
- Corporate use
:::
::::

## Implementation Roadmap

Based on the relevance assessment, here's a suggested implementation approach:

1. **Phase 1 - Essential Chapters** (Q1)
   - Focus on chapters with score 8/10
   - Direct implementation with minimal changes
   - Core banking supervision frameworks

2. **Phase 2 - Important Chapters** (Q2-Q3)
   - Adapt to Nigerian banking context
   - Customize for local market conditions
   - Integrate with existing CBN guidelines

3. **Phase 3 - Optional Chapters** (As needed)
   - Reference for specific regulatory gaps
   - Cherry-pick relevant sections
   - Use for comparative analysis

---

*Generated from UK FCA Consumer Credit Sourcebook analysis for CBN regulatory framework development.*

*Last updated: `r Sys.Date()`*